---
title: "text_processing_rap"
author: "Zhiyuan Zhang"
date: "2/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Step 1 - Load the data to be cleaned and processed

```{r}
# load lyrics data
load('../data/lyrics.RData') 
```

### Step 2 - Preliminary cleaning of text

We clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space.
Here we do not delete the dirty words, as well as some words that often appear in the hip-hop songs.

```{r text processing in tm}
# function for removimg leading and trailing whitespace from character strings 
leadingWhitespace <- content_transformer(function(x) str_trim(x, side = "both"))
# remove stop words
data("stop_words")
word <- c("lot", "today", "months", "month", "wouldnt", "wasnt", "ha", "na", "da", "gonna", "im", "dont", "aint", "wont", "la", "oi", "year", "years", "last", "past", "feel","yo","ya", "youre", "em")
stop_words <- c(stop_words$word, word)
# clean the data and make a corpus
corpus <- VCorpus(VectorSource(dt_lyrics$lyrics))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(removeWords, stop_words)%>%
  tm_map(removeNumbers)%>%
  tm_map(stripWhitespace)%>%
  tm_map(leadingWhitespace)
```

### Step 3 - Stemming words and converting tm object to tidy object

Stemming reduces a word to its word *stem*. We stem the words here and then convert the "tm" object to a "tidy" object for much faster processing.
```{r stemming}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

### Step 4 - Creating tidy format of the dictionary to be used for completing stems

We also need a dictionary to look up the words corresponding to the stems.

```{r tidy dictionary}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```


### Step 5 - Combining stems and dictionary into the same tibble

Here we combine the stems and the dictionary into the same "tidy" object.

```{r tidy stems with dictionary}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) 
```

### Step 6 - Stem completion

Lastly, we complete the stems by picking the corresponding word with the highest frequency.

```{r stem completion, warning=FALSE, message=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

### Step 8 - Pasting stem completed individual words into their respective lyrics

We want our processed words to resemble the structure of the original lyrics. So we paste the words together to form processed lyrics.

```{r reverse unnest}
completed <- completed %>%
  group_by(id) %>%
  summarise(stemmedwords= str_c(word, collapse = " ")) %>%
  ungroup()
```

### Step 9 - Keeping a track of the processed lyrics with their own ID

```{r cleaned hm_data, warning=FALSE, message=FALSE}
dt_lyrics <- dt_lyrics %>%
  mutate(id = row_number()) %>%
  inner_join(completed)
```

### Exporting the processed text data into a CSV file

```{r export data}
save(dt_lyrics, file="../output/processed_lyrics_rap.RData")
```





